---
title: "A Data-Oriented Unpacking of Global Hunger and Undernourishment"
author: "Samaya Badrieh, Natalie Stillwell, Desiree Vera, Nikhita Vaddineni"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dynamic Paragraph

Here is where to put the dynamic paragraph

## Table

Here is where to put the summary table

## Countries Where On Average, Half Of Children Under Five Are Stunted
```{r, include=FALSE}
# I could only get the chart to embed after I uploaded the source code 
source("../source/Graph_1.R")
```
```{r Graph_1, echo=FALSE}
#here is the 1st chart! Still needs some formatting to be integrated into P2
plot(most10_child_stunting)
```

We included this chart to show the places where food insecurity was affecting children the most. The data reveals that these seven countries - Bangladesh, Burundi, Eritrea, Guatemala, Madagascar, Timor, and Yemen - had on average 50% of their children's development stunted from malnutrition from 2015 to 2019. This is a shockingly high number, and this chart is important to show how severe the effects of hunger are on these populations and their youth.

## Millions Of People Severely Food Insecure People (2015-2019)
```{r, include=FALSE}
source("../source/Graph_2.R")
```
```{r Graph_2, echo=FALSE}
#Need to find a way to remove the geom_smooth note
plot(food_insecurity)
```

We included this chart to show how food insecurity had shifted over time. Our dataset only goes from 2015 to 2019, but it shows that despite some dips around 2017, by 2019 there were significantly more millions of people that were severely food insecure. This is important to note because it shows that food insecurity worldwide is getting worse with time, not better, and we need to get the root causes of it quickly or more people will continue to face hunger.

## Graph 3

```{r, include=FALSE}
source("../source/Graph_3.R")
```
```{r Graph_3, echo=FALSE}
plot(Top_10_graph)
```

We chose to include this chart in our report in order to demonstrate the
dynamics of the Global Hunger Index over time, specifically from the year 2000
to 2020, and in the top ten "hungriest" countries as determined by our earlier
analyses. In certain nations, such as Yemen and Madagascar, hunger appears to be
spiking. On the other hand, the other nations appear to be experiencing plateaus
and decreases. The main implication of this is that the changes in hunger
worldwide are not all following a single trend, and that different approaches
are called for in countries where trends in hunger, as well as its causes, are different.