---
title: "A Data-Oriented Unpacking of Global Hunger and Undernourishment"
author: "Samaya Badrieh, Natalie Stillwell, Desiree Vera, Nikhita Vaddineni"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dynamic Paragraph

Abstract
Our group was interested in exploring the relationship between world hunger and its major contributors. By using data from ourworldindata.org, we were able
to identify major patterns of where and when these contributions to global hunger occur. By analyzing our data we focus our concerns on the negative health
effects that come with hunger such as food insecurity, stunting in children, and the overall global hunger index contributers. By using location and the
years to see how the evidence of hunger patterns have increased or decreased, we can come up with potential solutions to address the food instability we
currently face. 

Introduction
One in four people globally are moderately or severely food insecure, which means that they lack consistent access to enough food to maintain an active,
healthy lifestyle. World Hunger has been on the rise in recent years, despite previously declining and our project aims to find out where this rise is
occurring the most. Good health and longevity rests on a foundation afforded by a diet which is both sufficient in caloric and nutritional value.
Unfortunately, undernourishment continues to be a leading risk factor for death and other health consequences. By examining the connections between hunger
and its causes and effects, a richness of knowledge can be extracted which can allow more urgency around the issue to spring forth, and encourage action
on the part of those possessing the means to incite change. According to Action Against Hunger, global food insecurity most directly affects the impoverished, young children, women, the most socially marginalized individuals, people in conflict settings, and refugees and the displaced. The benefits
of reducing world hunger include preventing its ability to ripple out and harm the development of nations, communities, and even individual humans (as
hunger stunts growth). The harms of approaching the issue are negiligible. 


## Table

| Summary Statistic | Values |
|-------------------|-----------|
| Country with the highest Global Health Index| Somalia |
|Country with the lowest Global Health Index | Belarus|
| Country with the highest child wasting percentage | Dijbouti|
| Country with the lowest child wasting percentage| United States |
|Country with the highest child stunting percentage| Ethiopia |
|Country with the lowest child stunting percentage | Germany |


## Countries Where On Average, Half Of Children Under Five Are Stunted
```{r, include=FALSE}
# I could only get the chart to embed after I uploaded the source code 
source("../source/Graph_1.R")
```
```{r Graph_1, echo=FALSE}
#here is the 1st chart! Still needs some formatting to be integrated into P2
plot(most10_child_stunting)
```

We included this chart to show the places where food insecurity was affecting children the most. The data reveals that these seven countries - Bangladesh, Burundi, Eritrea, Guatemala, Madagascar, Timor, and Yemen - had on average 50% of their children's development stunted from malnutrition from 2015 to 2019. This is a shockingly high number, and this chart is important to show how severe the effects of hunger are on these populations and their youth.

## Millions Of People Severely Food Insecure People (2015-2019)
```{r, include=FALSE}
source("../source/Graph_2.R")
```
```{r Graph_2, echo=FALSE}
#Need to find a way to remove the geom_smooth note
plot(food_insecurity)
```

We included this chart to show how food insecurity had shifted over time. Our dataset only goes from 2015 to 2019, but it shows that despite some dips around 2017, by 2019 there were significantly more millions of people that were severely food insecure. This is important to note because it shows that food insecurity worldwide is getting worse with time, not better, and we need to get the root causes of it quickly or more people will continue to face hunger.

## Graph 3

```{r, include=FALSE}
source("../source/Graph_3.R")
```
```{r Graph_3, echo=FALSE}
plot(Top_10_graph)
```

We chose to include this chart in our report in order to demonstrate the
dynamics of the Global Hunger Index over time, specifically from the year 2000
to 2020, and in the top ten "hungriest" countries as determined by our earlier
analyses. In certain nations, such as Yemen and Madagascar, hunger appears to be
spiking. On the other hand, the other nations appear to be experiencing plateaus
and decreases. The main implication of this is that the changes in hunger
worldwide are not all following a single trend, and that different approaches
are called for in countries where trends in hunger, as well as its causes, are different.
