---
title: "A Data-Oriented Unpacking of Global Hunger and Undernourishment"
author: "Samaya Badrieh, Natalie Stillwell, Desiree Vera, Nikhita Vaddineni"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dynamic Paragraph

Here is where to put the dynamic paragraph

## Table

Here is where to put the summary table

## Countries Where On Average, Half Of Children Under Five Are Stunted
```{r, include=FALSE}
# I could only get the chart to embed after I uploaded the source code 
source("../source/Graph_1.R")
```
```{r Graph_1, echo=FALSE}
#here is the 1st chart! Still needs some formatting to be integrated into P2
plot(most10_child_stunting)
```

We included this chart to show the places where food insecurity was affecting children the most. The data reveals that these seven countries - Bangladesh, Burundi, Eritrea, Guatemala, Madagascar, Timor, and Yemen - had on average 50% of their children's development stunted from malnutrition from 2015 to 2019. This is a shockingly high number, and this chart is important to show how severe the effects of hunger are on these populations and their youth.

## Millions Of People Severely Food Insecure People (2015-2019)
```{r, include=FALSE}
source("../source/Graph_2.R")
```
```{r Graph_2, echo=FALSE}
#Need to find a way to remove the geom_smooth note
plot(food_insecurity)
```

We included this chart to show how food insecurity had shifted over time. Our dataset only goes from 2015 to 2019, but it shows that despite some dips around 2017, by 2019 there were significantly more millions of people that were severely food insecure. This is important to note because it shows that food insecurity worldwide is getting worse with time, not better, and we need to get the root causes of it quickly or more people will continue to face hunger.

## Graph 3
Put chart here

Here is where to put the paragraph about the chart
